---
title: "Fin Chapter 7 Problem set"
output: html_document
date: "2024-09-30"
---

```{r setup, include=FALSE}

```

## R Markdown

#### a-1: Investment proportions in the minimum-variance portfolio

The weight of stock in the portfolio \( w_S \) is calculated using the formula:

$$
w_S = \frac{\sigma_B^2 - Cov(r_{s}, r_{b})}{\sigma_S^2 + \sigma_B^2 - 2 Cov(r_{s}, r_{b})}
$$
The weight of bonds in the portfolio \( w_B \) is:

$$
w_B = 1 - w_S
$$
```{r problem_1}
Ers=0.22 # Stock expected return
ErB=0.12 # Bond expected return
sds=0.32 # Stock standard deviation
sdB=0.19  # Bond standard deviation
p =0.11 #correlation coefficent
mmf=0.07 #money market fund that provides a safe return

#w_s =(.15**2 -.11*.32*.15)/ (.32**2 +.15**2 -2*.11*.32*.15)

w_s = ((sdB**2) - (p * sds * sdB)) / ((sds**2) + (sdB**2) - (2 * p * sds * sdB))
w_s


w_B =1- w_s
w_B
```




#### a-2: Expected return and standard deviation of the minimum-variance portfolio

The expected return of the minimum-variance portfolio \( E(R_p) \) is given by:

$$
E(R_p) = w_S E(R_S) + w_B E(R_B)
$$

The standard deviation of the minimum-variance portfolio \( \sigma_p \) is:

$$
\sigma_p = \sqrt{w_S^2 \sigma_S^2 + w_B^2 \sigma_B^2 + 2 w_S w_B \sigma_S \sigma_B \rho_{SB}}
$$

```{r Problem_1}
 
# Calculate expected return of the portfolio
Erp = w_s * Ers + w_B * ErB
cat("Expected Return of the Portfolio (Erp):", Erp) 

# Correct the formula for the standard deviation of the portfolio
sdp = (w_s**2 * sds**2 + w_B**2 * sdB**2 + 2 * w_s * w_B * sds * sdB * p) ** 0.5
cat("Standard Deviation of the Portfolio (sdp):", sdp)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
